\vspace{-0.5cm} XSGRB - The X-shooter GRB afterglow sample

### 2017-10-25 document/XSGRB_sample.tex
Final today
Conclusions

>>>>

All spectra have been made publicly available in the reduced form used
in this paper.

A number of independent papers have been published or submitted for publication
focusing on specific 
issues such as escape of ionizing radiation \citep{Tanvir17}, extinction
curves \citep{Jure16,Zafar17}, emission lines from the underlying host 
galaxies \citep{Kruhler2015}, more here.
